\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2018-02-19 redaction/dhp_july2017.tex
changement texte, encore

\textbf{stop here relecture}

@@

\textbf{VV: Nos resultats sont en ad-valorem (multiplicatif du prix), ce qui explique qu’on a des pourcentages superieurs pour Vessel par rapport a Air. Spontanement, on s’attend au contraire (les couts de fret sont plus importants dans l’aerien), mais en fait ces chiffres refletent simplement que les prix sont plus eleves dans l’aerien. En un mot, ces chiffres ne signifient pas que les couts monétaires dans l’aerien sont inférieurs au vessel. Ceci devrait etre precise. AMENDE LES RESULTATS DU TABLEAU POUR ESTIMER UNE VALEUR MONETAIRE + COMMENTAIRE (LIGHT) DESSUS. Ok ainsi?}

@@

Coming now to interpretation, two main results emerge from Table \ref{tab:summary_results}. First, it provides estimation results about the size of the overall transport costs. From Table \ref{tab:summary_results}, we obtain an overall value of approximatively a 6\% markup in ocean shipping, 5\% markup in air shipping in average over 1974-2013.\footnote{Expressed as a markup over production costs, transport costs are equal to $\frac{p-\widetilde{p}}{\widetilde{p}}$. Under Model (A) (ad-valorem costs only), making use of the figures reported in Table \ref{tab:summary_results} gives a markup of 5.8\% in vessel, and 5.1\% in air shipping (considering the mean value over the period). Under Model (B), total transport costs are equal to $\frac{p-\widetilde{p}}{\widetilde{p}} = (\tau-1) + \frac{t}{\widetilde{p}}$. With $\tau-1= 0.032$ and $\frac{t}{\widetilde{p}}= 0.029$ in Vessel (as reported in Table \ref{tab:summary_results}), we get a value equal to 6.1\% in Vessel. A similar calculus gives 4.3\% in air transport.} If this seems modest in comparison with the 11\% of markup obtained by \citet{anderson_wincoop_jel} over a set of industrialized countries, this stands in line with the results obtained by \citet{hummels2007} for the US economy. \footnote{The difference of results with \citet{anderson_wincoop_jel} can be accounted for by a number of reasons. \citet{anderson_wincoop_jel} obtain this 11\% markup as a rough value by aggregating various sources over a bunch of industrialized countries, with data mostly based on the second half of the 1990s. By contrast, our estimation of a 6\% markup relies on a single source of data based on the US imports flows over 1974-2013. Beyond country coverage and the time sample, another plausible candidate explanation lays in the difference of empirical methodology: \citet{anderson_wincoop_jel}'s estimates are based on standard gravity equations, while ours come from a non-linear estimation of a ``structural'' decomposition of the difference between export and import prices.}

Second, and most importantly, Table \ref{tab:summary_results} provides new quantitative evidence about the size of the additive component of transportation costs. We thus find that the per-kg cost dimension is quantitatively sizeable. On average over the whole period, additive costs are estimated to 2.9\% of the export price for ocean shipping, and 1.8\%. This is slightly lower than the estimates for the ad-valorem component, which is estimated to 3.2\% and 1.8\% for vessel and air shipping respectively (on average over the period). Put it differently, the additive component amounts to 48.2\% of total transport costs in Vessel, and 42.3\% in Air. Expressed in monetary terms, the additive cost of exporting amounts to around 10 cents and 1.12 USD per kilogram exported, in maritime and air transport cost respectively (at the 3-digit level), indicating that freight rates are much higher in air transport. For both transport modes, the omission of the additive term seriously biases the ad-valorem term upward. In quantitative terms, the omission of the additive term leads to overestimate the ad-valorem component by roughly a factor 2. Further, these results provide quantitative estimates for the values of both additive and ad-valorem transport costs, which can be very useful for the related more theoretical papers, which need to calibrate their models.\smallskip

@@

\textbf{VV: Les comparaisons chiffrees sont parfois délicates. Le paragraphe de comparaison avec Irarrazabal and co page 12 est tres clair, mais cela vient un peu tard. Il faut que des l’intro on comprenne bien la difference entre notre mesure de coûts additifs (representant entre 40 et 60\% des coûts de transport totaux) et les 14\% d’Irrara and co, qui sont un pourcentage du prix fab. MIS UN TOPO LA DESSUS EN INTRO. Ok AINSI?}

>>>>

@@

@@

Coming now to interpretation, two main results emerge from Table \ref{tab:summary_results}. First, it provides estimation results about the size of the overall transport costs. From Table \ref{tab:summary_results}, we obtain an overall value of approximatively a 6\% markup in ocean shipping, 5\% markup in air shipping in average over 1974-2013.\footnote{Expressed as a markup over production costs, transport costs are equal to $\frac{p-\widetilde{p}}{\widetilde{p}}$. Under Model (A) (ad-valorem costs only), making use of the figures reported in Table \ref{tab:summary_results} gives a markup of 5.8\% in vessel, and 5.1\% in air shipping (considering the mean value over the period). Under Model (B), total transport costs are equal to $\frac{p-\widetilde{p}}{\widetilde{p}} = (\tau-1) + \frac{t}{\widetilde{p}}$. With $\tau-1= 0.032$ and $\frac{t}{\widetilde{p}}= 0.029$ in Vessel (as reported in Table \ref{tab:summary_results}), we get a value equal to 6.1\% in Vessel. A similar calculus gives 4.3\% in air transport.} If this seems modest in comparison with the 11\% of markup obtained by \citet{anderson_wincoop_jel} over a set of industrialized countries, this stands in line with the results obtained by \citet{hummels2007} for the US economy.\footnote{The difference of results with \citet{anderson_wincoop_jel} can be accounted for by a number of reasons. \citet{anderson_wincoop_jel} obtain this 11\% markup as a rough value by aggregating various sources over a bunch of industrialized countries, with data mostly based on the second half of the 1990s. By contrast, our estimation of a 6\% markup relies on a single source of data based on the US imports flows over 1974-2013. Beyond country coverage and the time sample, another plausible candidate explanation lays in the difference of empirical methodology: \citet{anderson_wincoop_jel}'s estimates are based on standard gravity equations, while ours come from a non-linear estimation of a ``structural'' decomposition of the difference between export and import prices.}

Second, and most importantly, Table \ref{tab:summary_results} provides new quantitative evidence about the size of the additive component of transportation costs. On average over the whole period, additive costs are estimated to around 10 cents and 1.12 USD per kilogram exported, in maritime and air transport cost respectively (at the 3-digit level), indicating that freight rates are much higher in air transport. Expressed in terms of the export price, the additive costs amount to 2.9\% and 1.8 \% for ocean shipping and air transport respectively. This is slightly lower than the estimates for the ad-valorem component, which is estimated to 3.2\% and 1.8\% for vessel and air shipping respectively (on average over the period). Put it differently, the additive component amounts to 48.2\% of total transport costs in Vessel, and 42.3\% in Air. This shows that the per-kg cost dimension is quantitatively sizeable. For both transport modes, the omission of the additive term seriously biases the ad-valorem term upward, by roughly a factor 2. Further, these results provide quantitative estimates for the values of both additive and ad-valorem transport costs, which can be very useful for the related more theoretical papers, which need to calibrate their models.\smallskip

@@
